---
title: "Creating Calendars"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Creating Calendars}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

# Creating a calendars

Use `create.calendar` with your list of holidays.

```{r, echo=FALSE, message=FALSE}
library(bizdays)
holidays <- holidaysANBIMA
```

```{r, message=FALSE}
create.calendar(name='MyCalendar', holidays=holidays, weekdays=c('sunday', 'saturday'),
                adjust.from=adjust.next, adjust.to=adjust.previous)
```

what should be considered:

- calendar name: the calendar must be named `MyCalendar`. The calendar name is used in all `bizdays` functions to specify which calendar has to be used.
- list of holidays: the argument `holidays` is a vector of dates (mostly used R's date-time objects: `Date`, `POSIX.ct` and `POSIX.lt`) or a character vector with and ISO formatted date (`"1976-07-12"`).
- weekdays: weekdays to be treated as nonworking days (usually weekends).
- date adjustment: the `bizdays` function has `from` and `to` arguments that define the interval which the amount of days has to be computed. Once `from` falls in a nonworking day it is moved to the first working day after it. Similarly, `to` is adjusted to the first working day before this date.

Now you can call bizdays functions passing the calendar name.

```{r}
is.bizday('2016-07-12', 'MyCalendar')
following('2016-09-07', 'MyCalendar')
bizdays('2016-07-12', '2016-10-16', 'MyCalendar')
```

Of course you can assign the calendar to a variable directly and pass this variable to bizdays functions

```{r}
cal <- create.calendar(name='MyCalendar', holidays=holidays, weekdays=c('sunday', 'saturday'),
                       adjust.from=adjust.next, adjust.to=adjust.previous)
is.bizday('2016-07-12', cal)
```

But this is not expected to work that way.

> #### Why define weekdays?
> 
> I am frequently asked *Why do I have to define weekdays?* or even *Shouldn't it be `weekenddays` instead?*.
> 
> The reason I created `weekdays`:
> I want to provide a way to compute business days accordingly to any definition or satisfying any needs.
> In my world, the financial industry, weekends are nonworking days, but for those who work with events, for example, mondays migth be nonworking days.
> 
> `weekdays` defaults to `NULL` because I wanted the `Calendar()` call returned an [Actual](http://en.wikipedia.org/wiki/Day_count_convention#Actual_methods) calendar.

## Skiping weekends only (defining weekends as nonworking days)

You can define whatever calendar you want, for example, a calendar without holidays where only weekdays are nonworking days.

```{r, message=FALSE}
create.calendar(name='WeekendsOnly', weekdays=c('sunday', 'saturday'))
```

define only `weekdays` to weekend days.

```{r}
from_dates <- '2013-01-01'
to_dates <- seq(as.Date('2013-12-31'), as.Date('2020-12-31'), by='years')
bizdays(from_dates, to_dates, 'WeekendsOnly')
```

## Skiping mondays (defining mondays as nonworking days)

```{r}
create.calendar(name='EveryMonday', weekdays='monday')
from_dates <- '2013-01-01'
to_dates <- seq(as.Date('2013-12-31'), as.Date('2020-12-31'), by='years')
bizdays(from_dates, to_dates, 'EveryMonday')
```

## Skip nothing (formal current days calendar)

```{r}
create.calendar(name='Actual')
from_dates <- '2013-01-01'
to_dates <- seq(as.Date('2013-12-31'), as.Date('2020-12-31'), by='years')
bizdays(from_dates, to_dates, 'Actual')
```

