---
title: "Setting default calendar in .Rprofile"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Setting default calendar in .Rprofile}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---


# Setting default calendar in .Rprofile

That's the way I use `bizdays`, I set the `default.calendar` in my `.Rprofile`.
Since I am always using `holidaysANBIMA` holidays I create and set the default calendar in my `.Rprofile`.

```{r}
library(bizdays)
cal <- Calendar(holidays=holidaysANBIMA, name='ANBIMA', weekdays=c('saturday', 'sunday'), dib=252)
bizdays.options$set(default.calendar=cal)
```

If you put these 3 lines of code at the end of your `.Rprofile` you don't have to instantiate the calendar every time you use `bizdays`.
You can simply

```{r}
bizdays(from_dates, to_dates)
```

And it works with any of `bizdays` functions:

- `bizdays`, `bizdayse`
- `bizyears`, `bizyearse`
- `adjust.next`, `adjust.previous`
- `bizseq`
- `is.bizday`
- `offset`, `add.bizdays`
