---
title: "Using bizdays"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using bizdays}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

# Using bizdays

You start by defining a `Calendar` object.

```{r, message=FALSE}
library(bizdays)
cal <- Calendar(holidaysANBIMA, weekdays=c('sunday', 'saturday'), dib=252)
```

where `holidays` is a sequence of dates which represents **nonworking dates** and the second argument, `weekdays`, is a sequence with **nonworking weekdays**, so what `Calendar` does is define *gaps*.
`holidays` is a sequence of `Date` (or `POSIX*`) objects and 
`weekdays` must be a sequence of weekdays in words (lowercase).

Once you have instantiated a `Calendar` object you simply call `bizdays` function to get the amount of business days between 2 dates (or set of dates).

```{r}
from_dates <- c('2013-07-12', '2012-06-13')
to_dates <- seq(as.Date('2014-02-17'), as.Date('2016-07-21'), by='months')
bizdays(from_dates, to_dates, cal)
```

> #### Why define weekdays?
> 
> I am frequently asked *Why do I have to define weekdays?* or even *Shouldn't it be `weekenddays` instead?*.
> 
> The reason I created `weekdays`:
> I want to provide a way to compute business days accordingly to any definition or satisfying any needs.
> In my world, the financial industry, weekends are nonworking days, but for those who work with events, for example, mondays migth be nonworking days.
> 
> `weekdays` defaults to `NULL` because I wanted the `Calendar()` call returned an [Actual](http://en.wikipedia.org/wiki/Day_count_convention#Actual_methods) calendar.
> So calling `Calendar(dib=365, name='Actual/365')` returns an [Actual/365](http://en.wikipedia.org/wiki/Day_count_convention#Actual.2F365_Fixed) calendar.

